Improve SSD with Feature Fusion, \\IOU Loss and Super Resolution

### 2019-12-28 report/paper.tex
report template update
ssd baseline section update

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Improve SSD with Feature Fusion, \\IOU Loss and Data Augmentation}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% ljy
\section{SSD Baseline}

@@

>>>>

\usepackage{fontspec}

@@

\begin{document}

\newfontfamily\cl{Consolas}
\newcommand{\code}[1]{{\cl #1}}
% \newcommand{\code}[1]{#1}

%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Improve SSD with Feature Fusion, \\IOU Loss and Super Resolution}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

% ljy
\section{SSD Baseline}
Single Shot Multibox Detector (SSD) is an end-to-end convolutional neural network for object detection. The original paper \cite{ssd} demonstrates two variants of the model called the SSD300 and the SSD512. The suffixes represent the size of the input image. They have the same principles, although their structures have a slight difference.

As a baseline model, we choose SSD300 and reimplement it in PyTorch. The top functions of SSD network structure are shown in \code{ssd.py}. This section will focus on the structure of SSD network. The training and evaluation will be discussed in the experiment section.

% Unlike earlier architectures for object detection, e.g. RCNN, which consist of two distinct stages, a region proposal network that performs object localization and a classifier for detecting the types of objects in the proposed regions. However, they can be very computational expensive and therefore incapable of real-world, real-time applications. Single-shot models encapsulate both localization and detection tasks in a single network, resulting in significantly faster detections while deployable on lighter hardware.

\subsection{Network Structure Overview}
The whole SSD network can be organized into three parts

\subsubsection{Base convolutions}
It is derived from an existing image classification architecture that will provide lower-level feature maps.

SSD uses a modified VGG-16 as the base network. The first five blocks are a repetition of convolution, convolution and max pooling. Different from the original VGG-16, the remaining fully-connected layers (fc) are modified. FC8 is removed, and FC6 and FC7 are turned into convolutional layers. The base network will generate two feature maps of size $38$ and $19$ for later detection.

\subsubsection{Auxiliary convolutions}
They are added on top of the base network that will provide higher-level feature maps. SSD300 adds four extra convolution blocks to generate four more feature maps of size $10$, $5$, $3$, $1$.

\subsubsection{Prediction convolutions} layers that that will locate and identify objects in these feature maps, which will be discussed in more detail in the following.

All of these three structures are constructed in the function \code{multibox()}

\subsection{}

@@

\section{Experiments}
% ljy
\subsection{Dataset}

% chp
\subsection{Training}

% ljy
\subsection{Evaluation}

\subsection{Results}
